Forecasting the old-age dependency ratio to determine the best pension age

### 2020-05-03 PensionAge.tex
New Australian data

\usepackage{todonotes, xcolor}

@@

\section{Introduction}\label{introduction}

@@

In this paper, we use the OADR as a measure of the financial burden on
the Australian workforce because a rise in the OADR will reduce the
ability of working age population to finance pensions and health costs
\autocites{ARW07}{IGR02}{IGR07}. The OADR is defined as the ratio of the
number of people aged over the pension age to the number of people of
working age \autocite{ARW07}. This can be expressed using the formula
below:

\begin{equation}
  \text{OADR} = \frac{\text{number of people aged over pension age}}{\text{number of people aged 15 to pension age}}*100\%
\end{equation}

We provide forecasts of future population age structures over the next
50 years. We then use those forecasts to compute the OADR associated
with pension age both before and after the adjustments. One contribution
of the current study is the combined use of the Hyndman-Ullah
forecasting method \autocite{HU07} and the product-ratio method
\autocite{HBY13} to forecast a population age structure. Forecasts of
population structure have been built on forecasts of age- and
gender-specific mortality rates, fertility rates and net migration using
this method. These forecasts presuppose that the historical trends of
past years will continue. Historical data of those rates have thus been
used as input to simulate future paths of age- and gender-specific
population structure.

@@

\section{Background and Literature Review}\label{sec:litreview}

\subsection{The age pension in
Australia}\label{the-age-pension-in-australia}

@@

\subsection{Population forecasting}\label{population-forecasting}

@@

\subsubsection{Deterministic Methods Used by the
ABS}\label{deterministic-methods-used-by-the-abs}

@@

\subsubsection{Lee-Carter Method}\label{lee-carter-method}

@@

The model proposed by \textcite{LC92} is as follows:

\begin{equation}
  \ln(m_{x,t})=a_x+b_xk_t+\epsilon_{x,t}
\end{equation}

where \(m_{x,t}\) is the central death
rate\footnote{The central death rate is properly defined in Section~\ref{sec:data}}
for age \(x\) in year \(t\). This model involves fitting a matrix of log
central death rates with sets of age-specific constants, \{\(a_x\)\} and
\{\(b_x\)\}, and a time-varying index \(k_t\). \(b_x\) is a set of
parameters that tell us the rate at which each age responds to changes
in \(k_t\). \(k_t\) measures the general level of the log death rates;
\(a_x\) is the general pattern across age of the log mortality rate and
\(\epsilon_{x,t}\) is an error term with zero mean and constant
variance, reflecting the randomness that can't be captured by the model.

The model is under-determined in terms of estimation of parameters. For
example, if the vector \(a,b,k\) is one solution, then for any scalar
\(c\), \(a, b/c, kc\) or \(a - bc, b, k+c\) also must be two possible
solutions. Therefore, Lee and Carter (1992) impose the following
constraints:

\begin{equation}
  \sum_{t=1}^{n}k_t=0, \qquad \sum_{x=x_1}^{x_m}b_x=1
\end{equation}

Also, we normally seek the least squares solution when estimating
parameters. However, in this case, the model cannot be estimated using
simple regression methods because there is no regressor on the right
side of the equation. \textcite{LC92} choose a singular value
decomposition (SVD) method to undertake principal component analysis
(PCA), and hence find the least squares solution. It has been shown that
applying SVD method to a matrix of the logarithms of the rates after
subtracting the average over time of the log age-specific rates can find
the least square solution (Good, 1969). Therefore, the estimations of
\(b_x\) and \(k_t\) are the first principal component and scores of
\(\ln(m_{x,t})-a_x\) (i.e., \(b_x=\bm{z_1}\) and \(k_t=\bm{u_1}'\) when
\(\bm{X}=\ln(m_{x,t})-a_x\)). However, the empirical results suggest
that the resulting fitted number of deaths are biased estimates of
actual number of deaths because of the \(\ln\) transformation. To
overcome this problem, the LC method adjusts \(k_t\) such that for each
year, the implied number of deaths will be equal to the actual number of
deaths. The adjusted \(k_t\) is then extrapolated using random walk with
drift models, which is equivalent to ARIMA (\(0,1,0\)) model with
\(c\neq0\).

\subsubsection{\texorpdfstring{Hyndman-Ullah Method
\label{sec:HU}}{Hyndman-Ullah Method }}\label{hyndman-ullah-method}

@@

The model proposed by \textcite{HU07} is as follows: \vspace{-.3in}

\begin{align}
  y_t(x) & = s_t(x) + \sigma_t(x)\epsilon_{t,x}\label{eq:HU_1}\\
  s_t(x) & = \mu(x) + \sum_{j=1}^{J}\beta_{t,j}\phi_j(x) + e_t(x)\label{eq:HU_2}
\end{align}

Equation \eqref{eq:HU_1} describes the smoothing process. \(y_t(x)\) is
the observed data in year \(t\) and age \(x\), and \(s_t(x)\) is the
smoothed function of \(y_t(x)\), estimated by constrained weighted
penalized regression splines \autocite{BHT14}. \(\sigma_t(x)\) allows
the variance to be a function of time and age; and \(\epsilon_{t,x}\)
are independent identical distributed standard normal error terms.
Equation \eqref{eq:HU_2} has a similar structure to the LC method,
except that it incorporates more than one principal component and score.
It describes the dynamics of \(s_t(x)\) over time. The \(\beta_{t,j}\)
for every \(j\) and \(\mu(x)\) are sets of age-specific constants, and
\(\phi_j(x)\) for every \(j\) is a time-varying index. The \(e_t(x)\) is
the model error, which is the residual function with mean zero and no
serial correlation. The \(\mu(x)\) is estimated by the average of
\(s_t(x)\) across years, which measures the general shape of the
observed data \(y_t(x)\). The estimates of \(\phi_j(x)\) and
\(\beta_{t,j}\) are the \(j\)th principal component and scores of
\(s_t(x)-\mu(x)\) respectively. In other words, we take singular value
decomposition of \(s_t(x)-\mu(x)\), then \eqref{eq:HU_2} now becomes
\vspace{-.2in}

\begin{equation*}
  s_t(x)-\mu(x) = \phi_1(x)\beta_{t,1}+\phi_2(x)\beta_{t,2}+\dots+\phi_J(x)\beta_{t,J}
\end{equation*}

We chose \(J\) in a way that we believe the majority of information for
\(s_t(x)-\mu(x)\) has been captured by the first \(J\) components.

In terms of forecasting, by conditioning on the observed data
\(\bm{I}=\left\{{y_1(x),\dots,y_n(x)}\right\}\) and the set of
functional principal components
\(\bm{B}=\left\{{\phi_1(x),\phi_2(x),\dots,\phi_j(x)}\right\}\), the
\(h\)-step-ahead forecast of log rate \(y_{n+h}(x)\) can be acquired by:
\vspace{-.2in}

\begin{equation}
  \widehat{y}_{n+h\mid n}(x)=\widehat{s}_{n+h\mid n}(x) = \text{E}[\widehat{s}_{n+h\mid n}(x)\mid \bm{I, B}] = \widehat{\mu}(x)+\sum_{j=1}^{J}\phi_j(x)\widehat{\beta}_{n+h\mid n,j}
\end{equation}

where \(\widehat{\beta}_{n+h\mid n,j}\) denotes the \(h\)-step-ahead
forecast of \(\beta_{n+h\mid n,j}\). Because of the time-varying
property of \(\left\{\beta_{t,j}\right\}\), it controls the dynamics of
the process. For every component series \(\left\{\beta_{t,j}\right\}\),
we fit them with an ARIMA\((p_j,d_j,q_j)\) process, where
\(p_j,d_j,q_j\) are determined by minimizing the Akaike Information
Criterion (Booth, Hyndman \& Tickle, 2014). The fitted process is given
as follows: \vspace{-.3in}

\begin{equation*}
  (1-\phi_1B-\dots-\phi_{p_j}B^{p_j})(1-B)^{d_j}\beta_{t,j}=c+(1+\theta_1B+\dots+\theta_{q_j}B^{q_j})e_t, \quad ~\forall j=1,2,\dots,J,
\end{equation*}

where the parameters are estimated using maximum likelihood estimation.

\section{Data}\label{sec:data}

We use the same notation and similar procedures to construct data as in
\textcite{HB08}, because the fundamental model for forecasting
population for this study is the \textcite{HU07} method. The data used
to construct population age structure included: age- and gender-specific
birth and death numbers of each calendar year, age- and gender-specific
population members on 1~January of each year, and age- and
gender-specific exposures to risk (i.e., population of age \(x\) at 30
June) for each year. The notations are as follows: \vspace{-.4in}

\begin{align*}
  B_t(x) &= \text{Births in calendar year $t$ to females of age $x$}\\
  D_t(x) &= \text{Deaths in calendar year $t$ of persons of age $x$}\\
  P_t(x) &= \text{Population of age $x$ at 1 January of year $t$}\\
  E_t(x) &= \text{Population of age $x$ exposed to risk at 30 June of year $t$}\\
\end{align*}

\vspace{-.4in}where \(x\) denotes age and \(x=0,1,2,\dots,m^+\). \(m^+\)
is the open-ended upper age group, which is 100 in this study. \(t\)
denotes year and \(t=1,2,\dots,n\), where \(n\) is the horizon of
historical data used. Therefore, all of those data points can be
recorded in an \(m\times n\) matrix. The superscripts M and F denote
male and female respectively.

We can obtain historical mortality rates \(m_t(x)\) (also called central
death rates) and fertility rates \(f_t(x)\) as follows: \vspace{-.3in}

\begin{align*}
  m_t(x) & = \frac{D_t(x)}{E_t(x)}=\text{age-sex-specific central death rates in calendar year t}\\
  f_t(x) & = \frac{B_t(x)}{E^F_t(x)}=\text{age-specific fertility rates in calendar year t}
\end{align*}

In addition, the net
migration\footnote{Net migration is the difference between immigration and emigration in a certain area during a specified time frame}
(denoted \(G\)) is estimated using a demographic growth-balance
equation, which is an equation to summarize the relationship between
population change and three factors: net migration, births and deaths.
The equation is expressed as: \todo{Please define $p$ and $^+$}
\vspace{-.3in}

\begin{align*}
  G_t(x,x+1)     & =P_{t+1}(x+1)-P_t(x)+D_t(x,x+1)\text{~for~} x=0,1,2,\dots,p-2,\\
  G_t(p-1^+,p^+) & =P_{t+1}(p^+)-P_t(p^+)-P_t(p-1)+D_t(p-1^+,p^+)\\
  G_t(B,0)       & =P_{t+1}(0)-B_t+D_t(B,0)
\end{align*}

where \(G_t(x,x+1)\) refers to net migration in calendar year \(t\) of
persons aged \(x\) at beginning of year \(t\), \(G_t(p-1^+,p)\)
\todo{should it be $p^+$} refers to migration in calendar year \(t\) of
persons aged \(p-1\) and older at beginning of year \(t\), and
\(G_t(B,0)\) refers to deaths in calendar year \(t\) of births during
year \(t\); and similarly for deaths,
\(D_t(x,x+1), D_t(p-1^+,p^+), D_t(B,0)\). The deaths are estimated using
the standard life table approach of population projection. It should be
noted that the estimated net migration includes errors in data
recording.

@@

\subsection{Forecasting Population Age Structure and
OADR}\label{sec:forecasting}

@@

\subsubsection*{Step 1}\label{step-1}
\addcontentsline{toc}{subsubsection}{Step 1}

The main procedure for forecasting the population age structure follows
\textcite{HB08}, except that the data is updated, and we incorporate the
product-ratio method \autocite{HBY13} to improve the accuracy of the
forecast. The \textcite{HU07} model, introduced in section \ref{sec:HU},
is applied to the mortality rate, fertility rate and net migration
separately, based on the assumption that they behave independently.
Therefore, to fit the model to historical fertility rates, let
\(y_t(x)\) in equation \eqref{eq:HU_1} denote the observed historical
fertility data. However, for mortality rate by sex, the product-ratio
method is used to ensure the forecast of females and males are
non-divergent or coherent \autocite{HBY13}. In the product-ratio method,
after smoothing the female and male mortality rates, two other series
were created: product series (denoted by \(p_t(x)\)) and ratio series
(denoted by \(r_t(x)\)), which are defined as follows: \vspace{-.4in}

\begin{align}
  p_t(x)&=\sqrt{s_{t}^{\text{M}}(x)s_{t}^{\text{F}}(x)}, \label{eq:coherent_1}\\
  r_t(x)&=\sqrt{\frac{s_{t}^{\text{M}}(x)}{s_{t}^{\text{F}}(x)}}. \label{eq:coherent_2}
\end{align}

Then, \textcite{HU07} was applied to these two new variables instead of
male and female mortality rate as follows: \vspace{-.3in}

\begin{align*}
  \ln[p_t(x)]=\mu_p(x)+\sum_{j=1}^{J}\beta_{t,j}\phi_j(x)+e_t(x)\\
  \ln[r_t(x)]=\mu_r(x)+\sum_{l=1}^{L}\gamma_{t,l}\psi_l(x)+z_t(x)
\end{align*}

where time series \(\left\{\beta_{t,j}\right\}\) are fitted with an
ARIMA model while \(\left\{\gamma_{t,l}\right\}\) are fitted by
stationary ARFIMA model (i.e., \(d\) in ARIMA(\(p,d,q\)) constrained to
\(0<d<\frac{1}{2}\)). It is the stationary constraint on
\(\gamma_{t,l}\) that ensures the forecast of male and female do not
diverge. Then, simulating \(h\)-step-ahead forecast values of product
variable and ratio variable was performed (denoted by
\(p_{n+h\mid n}(x)\) and \(r_{n+h\mid n}(x)\) respectively) according to
\eqref{eq:coherent_1} and \eqref{eq:coherent_2}. From here, obtaining
\(h\)-step-ahead forecast of sex-specific coherent mortality rates
(denoted \(m_{n+h\mid n,M}(x)\) and \(m_{n+h\mid n,F}(x)\)) was
performed using a back-transformation: \vspace{-.3in}

\begin{align*}
  m_{n+h\mid n}^{\text{M}}(x) & = p_{n+h\mid n}(x)r_{n+h\mid n}(x)\\
  m_{n+h\mid n}^{\text{F}}(x) & = p_{n+h\mid n}(x)/r_{n+h\mid n}(x)
\end{align*}

The method for simulating \(h\)-step-ahead values of net migration by
sex is similar to the above method used on mortality rates except no log
scale is applied to net migration. A stationary constraint was imposed
on the ARIMA model for net migration to make sure the difference between
sexes did not diverge.

\subsubsection*{Step 2}\label{step-2}
\addcontentsline{toc}{subsubsection}{Step 2}

@@

\subsubsection*{Step 3}\label{step-3}
\addcontentsline{toc}{subsubsection}{Step 3}

@@

Suppose the pension age for \(n+1\) is \(a.r\) where \(a\) is the
integer and and \(r\) is the reminder of pension age. Recall that for
\(h=1\), we can express the simulated population paths as a matrix with
age in the row and simulation in the column as follows:

\begin{equation*}
  \bm{p}_{n+1}=[p_{n+1,m,i}] =
    \begin{bmatrix}
       p_{1,1} & \cdots\cdots & p_{1,1000} \\
      \vdots & \ddots & \vdots \\
      p_{100^+,1} & \cdots\cdots &p_{100^+,1000}
      \end{bmatrix}.
\end{equation*}

When \(r=0\), then the simulation of a population aged 15 to pension age
is a subset of the above matrix from \(15^{th}\) row to \(a-1^{th}\)
row, which is:

\begin{equation}
  \begin{bmatrix}
    p_{15,1} & \cdots\cdots & p_{15,1000} \\
    \vdots & \ddots & \vdots \\
    p_{a-1,1} & \cdots\cdots &p_{a-1,1000}
  \end{bmatrix}. \label{eq:population_mat}
\end{equation}

To calculate the total number of working age, we take a column sum of
the trimmed matrix \eqref{eq:population_mat}. The simulations of total
number of work age become a vector:

\begin{equation}
  \bm{p}^{\text{work}}_{n+1} = \left[\sum_{m=15}^{a-1}p_{m,1},\sum_{m=15}^{a-1}p_{m,2},\dots,\sum_{m=15}^{a-1}p_{m,1000}\right] \label{eq:work}
\end{equation}

Using the same method, the simulations of total number of aged
pensioners in the population can be shown as:

\begin{equation}
  \bm{p}^{\text{aged}}_{n+1} = \left[\sum_{m=a}^{100^+}p_{m,1},\sum_{m=a}^{100^+}p_{m,2},\dots,\sum_{m=a}^{100^+}p_{m,1000}\right]\label{eq:aged}
\end{equation}

When \(r\neq0\), the vector of total number of working age population in
\eqref{eq:work} is added, and the vector of total number of aged
population in \eqref{eq:aged} is subtracted with an adjustment:
\vspace{-.2in}

\begin{equation}
  \text{adjustment}=0.r\times100\%[p_{a,1},p_{a,2},\dots,p_{a,1000}]
\end{equation}

This adjustment is based on the assumption that the birthday of
population is uniformly distributed over the year. Then,
\(r\times100\%\) of population with a recorded integer age of \(a\) at
beginning of the year is actually younger than \(a.r\), so they are
still under the pension age. In other words, \((1-r\times100\%)\) of
population with recorded integer age \(a\) at beginning of the year is
actually older than \(a.r\), so they should be counted as the aged
population. The simulation vectors of total work age population and
total aged population should then be:

>>>>

\usepackage{todonotes, xcolor}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

In this paper, we use the OADR as a measure of the financial burden on the Australian workforce because a rise in the OADR will reduce the ability of working age population to finance pensions and health costs \autocites{ARW07}{IGR02}{IGR07}. The OADR is defined as the ratio of the number of people aged over the pension age to the number of people of working age \autocite{ARW07}. This can be expressed using the formula below:
\begin{equation}
  \text{OADR} = \frac{\text{number of people aged over pension age}}{\text{number of people aged 15 to pension age}}*100\%
\end{equation}
We provide forecasts of future population age structures over the next 50 years. We then use those forecasts to compute the OADR associated with pension age both before and after the adjustments. One contribution of the current study is the combined use of the Hyndman-Ullah forecasting method \autocite{HU07} and the product-ratio method \autocite{HBY13} to forecast a population age structure. Forecasts of population structure have been built on forecasts of age- and gender-specific mortality rates, fertility rates and net migration using this method. These forecasts presuppose that the historical trends of past years will continue. Historical data of those rates have thus been used as input to simulate future paths of age- and gender-specific population structure.

@@

\hypertarget{sec:litreview}{%
\section{Background and Literature Review}\label{sec:litreview}}

\hypertarget{the-age-pension-in-australia}{%
\subsection{The age pension in Australia}\label{the-age-pension-in-australia}}

@@

\hypertarget{population-forecasting}{%
\subsection{Population forecasting}\label{population-forecasting}}

@@

\hypertarget{deterministic-methods-used-by-the-abs}{%
\subsubsection{Deterministic Methods Used by the ABS}\label{deterministic-methods-used-by-the-abs}}

@@

\hypertarget{lee-carter-method}{%
\subsubsection{Lee-Carter Method}\label{lee-carter-method}}

@@

The model proposed by \textcite{LC92} is as follows:
\begin{equation}
  \ln(m_{x,t})=a_x+b_xk_t+\epsilon_{x,t}
\end{equation}
where \(m_{x,t}\) is the central death rate\footnote{The central death rate is properly defined in Section~\ref{sec:data}} for age \(x\) in year \(t\). This model involves fitting a matrix of log central death rates with sets of age-specific constants, \{\(a_x\)\} and \{\(b_x\)\}, and a time-varying index \(k_t\). \(b_x\) is a set of parameters that tell us the rate at which each age responds to changes in \(k_t\). \(k_t\) measures the general level of the log death rates; \(a_x\) is the general pattern across age of the log mortality rate and \(\epsilon_{x,t}\) is an error term with zero mean and constant variance, reflecting the randomness that can't be captured by the model.

The model is under-determined in terms of estimation of parameters. For example, if the vector \(a,b,k\) is one solution, then for any scalar \(c\), \(a, b/c, kc\) or \(a - bc, b, k+c\) also must be two possible solutions. Therefore, Lee and Carter (1992) impose the following constraints:
\begin{equation}
  \sum_{t=1}^{n}k_t=0, \qquad \sum_{x=x_1}^{x_m}b_x=1
\end{equation}
Also, we normally seek the least squares solution when estimating parameters. However, in this case, the model cannot be estimated using simple regression methods because there is no regressor on the right side of the equation. \textcite{LC92} choose a singular value decomposition (SVD) method to undertake principal component analysis (PCA), and hence find the least squares solution. It has been shown that applying SVD method to a matrix of the logarithms of the rates after subtracting the average over time of the log age-specific rates can find the least square solution (Good, 1969). Therefore, the estimations of \(b_x\) and \(k_t\) are the first principal component and scores of \(\ln(m_{x,t})-a_x\) (i.e., \(b_x=\bm{z_1}\) and \(k_t=\bm{u_1}'\) when \(\bm{X}=\ln(m_{x,t})-a_x\)). However, the empirical results suggest that the resulting fitted number of deaths are biased estimates of actual number of deaths because of the \(\ln\) transformation. To overcome this problem, the LC method adjusts \(k_t\) such that for each year, the implied number of deaths will be equal to the actual number of deaths. The adjusted \(k_t\) is then extrapolated using random walk with drift models, which is equivalent to ARIMA (\(0,1,0\)) model with \(c\neq0\).

\hypertarget{hyndman-ullah-method}{%
\subsubsection{\texorpdfstring{Hyndman-Ullah Method \label{sec:HU}}{Hyndman-Ullah Method }}\label{hyndman-ullah-method}}

@@

The model proposed by \textcite{HU07} is as follows:
\vspace{-.3in}
\begin{align}
  y_t(x) & = s_t(x) + \sigma_t(x)\epsilon_{t,x}\label{eq:HU_1}\\
  s_t(x) & = \mu(x) + \sum_{j=1}^{J}\beta_{t,j}\phi_j(x) + e_t(x)\label{eq:HU_2}
\end{align}
Equation \eqref{eq:HU_1} describes the smoothing process. \(y_t(x)\) is the observed data in year \(t\) and age \(x\), and \(s_t(x)\) is the smoothed function of \(y_t(x)\), estimated by constrained weighted penalized regression splines \autocite{BHT14}. \(\sigma_t(x)\) allows the variance to be a function of time and age; and \(\epsilon_{t,x}\) are independent identical distributed standard normal error terms. Equation \eqref{eq:HU_2} has a similar structure to the LC method, except that it incorporates more than one principal component and score. It describes the dynamics of \(s_t(x)\) over time. The \(\beta_{t,j}\) for every \(j\) and \(\mu(x)\) are sets of age-specific constants, and \(\phi_j(x)\) for every \(j\) is a time-varying index. The \(e_t(x)\) is the model error, which is the residual function with mean zero and no serial correlation. The \(\mu(x)\) is estimated by the average of \(s_t(x)\) across years, which measures the general shape of the observed data \(y_t(x)\). The estimates of \(\phi_j(x)\) and \(\beta_{t,j}\) are the \(j\)th principal component and scores of \(s_t(x)-\mu(x)\) respectively. In other words, we take singular value decomposition of \(s_t(x)-\mu(x)\), then \eqref{eq:HU_2} now becomes
\vspace{-.2in}
\begin{equation*}
  s_t(x)-\mu(x) = \phi_1(x)\beta_{t,1}+\phi_2(x)\beta_{t,2}+\dots+\phi_J(x)\beta_{t,J}
\end{equation*}
We chose \(J\) in a way that we believe the majority of information for \(s_t(x)-\mu(x)\) has been captured by the first \(J\) components.

In terms of forecasting, by conditioning on the observed data \(\bm{I}=\left\{{y_1(x),\dots,y_n(x)}\right\}\) and the set of functional principal components \(\bm{B}=\left\{{\phi_1(x),\phi_2(x),\dots,\phi_j(x)}\right\}\), the \(h\)-step-ahead forecast of log rate \(y_{n+h}(x)\) can be acquired by:
\vspace{-.2in}
\begin{equation}
  \widehat{y}_{n+h\mid n}(x)=\widehat{s}_{n+h\mid n}(x) = \text{E}[\widehat{s}_{n+h\mid n}(x)\mid \bm{I, B}] = \widehat{\mu}(x)+\sum_{j=1}^{J}\phi_j(x)\widehat{\beta}_{n+h\mid n,j}
\end{equation}
where \(\widehat{\beta}_{n+h\mid n,j}\) denotes the \(h\)-step-ahead forecast of \(\beta_{n+h\mid n,j}\). Because of the time-varying property of \(\left\{\beta_{t,j}\right\}\), it controls the dynamics of the process. For every component series \(\left\{\beta_{t,j}\right\}\), we fit them with an ARIMA\((p_j,d_j,q_j)\) process, where \(p_j,d_j,q_j\) are determined by minimizing the Akaike Information Criterion (Booth, Hyndman \& Tickle, 2014). The fitted process is given as follows:
\vspace{-.3in}
\begin{equation*}
  (1-\phi_1B-\dots-\phi_{p_j}B^{p_j})(1-B)^{d_j}\beta_{t,j}=c+(1+\theta_1B+\dots+\theta_{q_j}B^{q_j})e_t, \quad ~\forall j=1,2,\dots,J,
\end{equation*}
where the parameters are estimated using maximum likelihood estimation.

\hypertarget{sec:data}{%
\section{Data}\label{sec:data}}

We use the same notation and similar procedures to construct data as in \textcite{HB08}, because the fundamental model for forecasting population for this study is the \textcite{HU07} method. The data used to construct population age structure included: age- and gender-specific birth and death numbers of each calendar year, age- and gender-specific population members on 1~January of each year, and age- and gender-specific exposures to risk (i.e., population of age \(x\) at 30 June) for each year. The notations are as follows:
\vspace{-.4in}
\begin{align*}
  B_t(x) &= \text{Births in calendar year $t$ to females of age $x$}\\
  D_t(x) &= \text{Deaths in calendar year $t$ of persons of age $x$}\\
  P_t(x) &= \text{Population of age $x$ at 1 January of year $t$}\\
  E_t(x) &= \text{Population of age $x$ exposed to risk at 30 June of year $t$}\\
\end{align*}
\vspace{-.4in}where \(x\) denotes age and \(x=0,1,2,\dots,m^+\). \(m^+\) is the open-ended upper age group, which is 100 in this study. \(t\) denotes year and \(t=1,2,\dots,n\), where \(n\) is the horizon of historical data used. Therefore, all of those data points can be recorded in an \(m\times n\) matrix. The superscripts M and F denote male and female respectively.

We can obtain historical mortality rates \(m_t(x)\) (also called central death rates) and fertility rates \(f_t(x)\) as follows:
\vspace{-.3in}
\begin{align*}
  m_t(x) & = \frac{D_t(x)}{E_t(x)}=\text{age-sex-specific central death rates in calendar year t}\\
  f_t(x) & = \frac{B_t(x)}{E^F_t(x)}=\text{age-specific fertility rates in calendar year t}
\end{align*}

In addition, the net migration\footnote{Net migration is the difference between immigration and emigration in a certain area during a specified time frame} (denoted \(G\)) is estimated using a demographic growth-balance equation, which is an equation to summarize the relationship between population change and three factors: net migration, births and deaths. The equation is expressed as: \todo{Please define $p$ and $^+$}
\vspace{-.3in}
\begin{align*}
  G_t(x,x+1)     & =P_{t+1}(x+1)-P_t(x)+D_t(x,x+1)\text{~for~} x=0,1,2,\dots,p-2,\\
  G_t(p-1^+,p^+) & =P_{t+1}(p^+)-P_t(p^+)-P_t(p-1)+D_t(p-1^+,p^+)\\
  G_t(B,0)       & =P_{t+1}(0)-B_t+D_t(B,0)
\end{align*}
where \(G_t(x,x+1)\) refers to net migration in calendar year \(t\) of persons aged \(x\) at beginning of year \(t\), \(G_t(p-1^+,p)\) \todo{should it be $p^+$} refers to migration in calendar year \(t\) of persons aged \(p-1\) and older at beginning of year \(t\), and \(G_t(B,0)\) refers to deaths in calendar year \(t\) of births during year \(t\); and similarly for deaths, \(D_t(x,x+1), D_t(p-1^+,p^+), D_t(B,0)\). The deaths are estimated using the standard life table approach of population projection. It should be noted that the estimated net migration includes errors in data recording.

@@

\hypertarget{sec:forecasting}{%
\subsection{Forecasting Population Age Structure and OADR}\label{sec:forecasting}}

@@

\hypertarget{step-1}{%
\subsubsection*{Step 1}\label{step-1}}
\addcontentsline{toc}{subsubsection}{Step 1}

The main procedure for forecasting the population age structure follows \textcite{HB08}, except that the data is updated, and we incorporate the product-ratio method \autocite{HBY13} to improve the accuracy of the forecast. The \textcite{HU07} model, introduced in section \ref{sec:HU}, is applied to the mortality rate, fertility rate and net migration separately, based on the assumption that they behave independently. Therefore, to fit the model to historical fertility rates, let \(y_t(x)\) in equation \eqref{eq:HU_1} denote the observed historical fertility data. However, for mortality rate by sex, the product-ratio method is used to ensure the forecast of females and males are non-divergent or coherent \autocite{HBY13}. In the product-ratio method, after smoothing the female and male mortality rates, two other series were created: product series (denoted by \(p_t(x)\)) and ratio series (denoted by \(r_t(x)\)), which are defined as follows:
\vspace{-.4in}
\begin{align}
  p_t(x)&=\sqrt{s_{t}^{\text{M}}(x)s_{t}^{\text{F}}(x)}, \label{eq:coherent_1}\\
  r_t(x)&=\sqrt{\frac{s_{t}^{\text{M}}(x)}{s_{t}^{\text{F}}(x)}}. \label{eq:coherent_2}
\end{align}
Then, \textcite{HU07} was applied to these two new variables instead of male and female mortality rate as follows:
\vspace{-.3in}
\begin{align*}
  \ln[p_t(x)]=\mu_p(x)+\sum_{j=1}^{J}\beta_{t,j}\phi_j(x)+e_t(x)\\
  \ln[r_t(x)]=\mu_r(x)+\sum_{l=1}^{L}\gamma_{t,l}\psi_l(x)+z_t(x)
\end{align*}
where time series \(\left\{\beta_{t,j}\right\}\) are fitted with an ARIMA model while \(\left\{\gamma_{t,l}\right\}\) are fitted by stationary ARFIMA model (i.e., \(d\) in ARIMA(\(p,d,q\)) constrained to \(0<d<\frac{1}{2}\)). It is the stationary constraint on \(\gamma_{t,l}\) that ensures the forecast of male and female do not diverge. Then, simulating \(h\)-step-ahead forecast values of product variable and ratio variable was performed (denoted by \(p_{n+h\mid n}(x)\) and \(r_{n+h\mid n}(x)\) respectively) according to \eqref{eq:coherent_1} and \eqref{eq:coherent_2}. From here, obtaining \(h\)-step-ahead forecast of sex-specific coherent mortality rates (denoted \(m_{n+h\mid n,M}(x)\) and \(m_{n+h\mid n,F}(x)\)) was performed using a back-transformation:
\vspace{-.3in}
\begin{align*}
  m_{n+h\mid n}^{\text{M}}(x) & = p_{n+h\mid n}(x)r_{n+h\mid n}(x)\\
  m_{n+h\mid n}^{\text{F}}(x) & = p_{n+h\mid n}(x)/r_{n+h\mid n}(x)
\end{align*}
The method for simulating \(h\)-step-ahead values of net migration by sex is similar to the above method used on mortality rates except no log scale is applied to net migration. A stationary constraint was imposed on the ARIMA model for net migration to make sure the difference between sexes did not diverge.

\hypertarget{step-2}{%
\subsubsection*{Step 2}\label{step-2}}
\addcontentsline{toc}{subsubsection}{Step 2}

@@

\hypertarget{step-3}{%
\subsubsection*{Step 3}\label{step-3}}
\addcontentsline{toc}{subsubsection}{Step 3}

@@

Suppose the pension age for \(n+1\) is \(a.r\) where \(a\) is the integer and and \(r\) is the reminder of pension age. Recall that for \(h=1\), we can express the simulated population paths as a matrix with age in the row and simulation in the column as follows:
\begin{equation*}
  \bm{p}_{n+1}=[p_{n+1,m,i}] =
    \begin{bmatrix}
       p_{1,1} & \cdots\cdots & p_{1,1000} \\
      \vdots & \ddots & \vdots \\
      p_{100^+,1} & \cdots\cdots &p_{100^+,1000}
      \end{bmatrix}.
\end{equation*}
When \(r=0\), then the simulation of a population aged 15 to pension age is a subset of the above matrix from \(15^{th}\) row to \(a-1^{th}\) row, which is:
\begin{equation}
  \begin{bmatrix}
    p_{15,1} & \cdots\cdots & p_{15,1000} \\
    \vdots & \ddots & \vdots \\
    p_{a-1,1} & \cdots\cdots &p_{a-1,1000}
  \end{bmatrix}. \label{eq:population_mat}
\end{equation}
To calculate the total number of working age, we take a column sum of the trimmed matrix \eqref{eq:population_mat}. The simulations of total number of work age become a vector:
\begin{equation}
  \bm{p}^{\text{work}}_{n+1} = \left[\sum_{m=15}^{a-1}p_{m,1},\sum_{m=15}^{a-1}p_{m,2},\dots,\sum_{m=15}^{a-1}p_{m,1000}\right] \label{eq:work}
\end{equation}
Using the same method, the simulations of total number of aged pensioners in the population can be shown as:
\begin{equation}
  \bm{p}^{\text{aged}}_{n+1} = \left[\sum_{m=a}^{100^+}p_{m,1},\sum_{m=a}^{100^+}p_{m,2},\dots,\sum_{m=a}^{100^+}p_{m,1000}\right]\label{eq:aged}
\end{equation}

When \(r\neq0\), the vector of total number of working age population in \eqref{eq:work} is added, and the vector of total number of aged population in \eqref{eq:aged} is subtracted with an adjustment:
\vspace{-.2in}
\begin{equation}
  \text{adjustment}=0.r\times100\%[p_{a,1},p_{a,2},\dots,p_{a,1000}]
\end{equation}
This adjustment is based on the assumption that the birthday of population is uniformly distributed over the year. Then, \(r\times100\%\) of population with a recorded integer age of \(a\) at beginning of the year is actually younger than \(a.r\), so they are still under the pension age. In other words, \((1-r\times100\%)\) of population with recorded integer age \(a\) at beginning of the year is actually older than \(a.r\), so they should be counted as the aged population. The simulation vectors of total work age population and total aged population should then be:
\begin{align*}
  \bm{p}^{\text{work}}_{n+1}
    & = \left[p^{\text{work}}_{n+1,1},p^{\text{work}}_{n+1,2},\dots,p^{\text{work}}_{n+1,1000}\right]\\
    & = \left[\sum_{m=15}^{a-1}p_{m,1},\sum_{m=15}^{a-1}p_{m,2},\dots,\sum_{m=15}^{a-1}p_{m,1000}\right]+0.r\times100\%\left[p_{a,1},p_{a,2},\dots,p_{a,1000}\right]   \\
  \bm{p}^{\text{aged}}_{n+1}
    & = \left[p^{\text{aged}}_{n+1,1},p^{\text{aged}}_{n+1,2},\dots,p^{\text{aged}}_{n+1,1000}\right]\\
    & = \left[\sum_{m=a}^{100^+}p_{m,1},\sum_{m=a}^{100^+}p_{m,2},\dots,\sum_{m=a}^{100^+}p_{m,1000}\right]-0.r\times100\%\left[p_{a,1},p_{a,2},\dots,p_{a,1000}\right]
\end{align*}
